A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-13 PPSN2016/paper.Rnw
Reprocessed files
Added a new column with "reboots" and nothing seems to be broken, so...
Answering @mariosky suggestions
Adding data per IP to the paper script
It looks like there is a certain difference, with nnumber of reboots going up depending on the presentation. I will have to do a Wilcoxon difference or something

experiment.aggregates <- data.frame(Experiment=character(),
                                    milliseconds=character(),
                                    IPs=character(),
                                    actualIPs = character(),
                                    PUTss = character(),
                                    actualPUTs = character(),
                                    count = character())

@@

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-per-minute-cache=32-",i,".csv"))
    this.data.plus1 <- this.data[2:length(this.data$IPs),]
    ip.correlations <- rbind(ip.correlations, 
                             data.frame(Experiment=i,
                                        correlation = cor(this.data[c(1:length(this.data$IPs)-1),]$IPs
                                                         ,this.data.plus1$IPs)))
    time.data <- rbind(time.data,
                       data.frame(Experiment=rep(i,length(this.data$IPs)),
                                  minute=strptime(this.data$time,"%Y-%m-%d %H:%M"),
                                  IPs=as.integer(this.data$IPs))
                       )
}
@

@@

The architecture of the {\sf NodIO} system is divided in two tiers:\begin{enumerate}
\item A REST (representational state transfer) server that responds to
  HTTP requests made by the browsers. These HTTP requests use JSON for
  encoding information, in this case chromosomes and associates
  information send by the clients and return requests made by the
  server.  The server has the capability to
  run a single experiment, storing the incoming chromosomes in a cache data structure
  that is reset when the solution is found. This data has a finite
  size that erases the oldest chromosomes once it has filled to
  capacity.  
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays the fitness and
  other graphs, some
  additional links, and information on the experiment. This code runs
  an evolutionary algorithm {\em island} that starts with a random
  population, then after every 100 generations, it sends the best individual
  back to the server (via a {\tt PUT} request), and then requests a random
  individual back from the server (via a {\tt GET} request). We have
  kept the number of generations between migrations fixed since it is
  a way of finding out how much real work every client is doing. In
  the version of the server used in this paper, we implemented a
  policy by which the combination IP-fitness value could only be
  inserted once into the cache. That means that if a particular IP
  sends the fitness 99 into the server, it will be accepted only
  once. The main intention of this policy was to avoid {\em
    overlapping} of contributions, with clients still running an {\em
    old} run of the experiment contributing after a new one had
  started. This did not completely avoid these contributions: if the
  clients of the {\em old} run increased their new fitness, it would
  still be allowed. 
  % As I remember we kept the run_number so IPs with old runs
  % did not interfere with newer ones. But you are saying: what if they are super slow 
  % and always PUT when the run is already over?, we want to receive 
  % those individuals? 
  % "That means that if a particular IP
  % sends the fitness 99 into the server, it will be accepted only
  % once."  
  % once per run?
  %  but different individuals could have the same fitness, are we limiting the search? 
  %  maybe we could have multiple versions of the pool a la MVCC  :)
  % I think if we are just trying to limit overlapping of the experiments
  % then PUTs should send the run's seq_number and completly remove it.

\end{enumerate}

@@

>>>>

experiment.aggregates <- data.frame(Experiment=character(),
                                    milliseconds=character(),
                                    IPs=character(),
                                    actualIPs = character(),
                                    PUTs = character(),
                                    actualPUTs = character(),
                                    count = character())

@@

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-per-minute-cache=32-",i,".csv"))
    this.data.plus1 <- this.data[2:length(this.data$IPs),]
    ip.correlations <- rbind(ip.correlations, 
                             data.frame(Experiment=i,
                                        correlation = cor(this.data[c(1:length(this.data$IPs)-1),]$IPs
                                                         ,this.data.plus1$IPs)))
    time.data <- rbind(time.data,
                       data.frame(Experiment=rep(i,length(this.data$IPs)),
                                  minute=strptime(this.data$time,"%Y-%m-%d %H:%M"),
                                  IPs=as.integer(this.data$IPs))
                       )
}

ips.data <- data.frame(Experiment=character(),                      
                       PUTs=character(),
                       reboots=character())

ips.aggregates <- data.frame(Experiment=character(),
                             PUTs = character(),
                             reboots = character(),
                             avgPUTs = character(),
                             avgreboots = character() )

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-reboots-cache=32-",i,".csv"))
    ips.data <- rbind(ips.data,
                      data.frame(Experiment=rep(i,length(this.data$PUTs)),
                                 PUTs=as.integer(this.data$PUTs),
                                 reboots=as.integer(this.data$reboots))
                       )

    ips.aggregates <- rbind( ips.aggregates,
                            data.frame(Experiment=i,
                                       PUTs = median(this.data$PUTs),
                                       reboots = median(this.data$reboots),
                                       avgPUTs = mean(this.data$PUTs),
                                       avgreboots = mean(this.data$reboots) )
                            )
}
@

@@

The architecture of the {\sf NodIO} system is divided in two tiers:\begin{enumerate}
\item A REST (representational state transfer) server that responds to
  HTTP requests made by the browsers. These HTTP requests use JSON for
  encoding information, in this case chromosomes and associates
  information send by the clients and return requests made by the
  server.  The server has the capability to
  run a single experiment, storing the incoming chromosomes in a cache data structure
  that is reset when the solution is found. This data has a finite
  size that erases the oldest chromosomes once it has filled to
  capacity.  
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays the fitness and
  other graphs, some
  additional links, and information on the experiment. This code runs
  an evolutionary algorithm {\em island} that starts with a random
  population, then after every 100 generations, it sends the best individual
  back to the server (via a {\tt PUT} request), and then requests a random
  individual back from the server (via a {\tt GET} request). We have
  kept the number of generations between migrations fixed since it is
  a way of finding out how much real work every client is doing. In
  the version of the server used in this paper, we implemented a
  policy by which the combination IP-fitness value could only be
  inserted once into the cache. That means that if a particular IP
  sends the fitness 99 into the server, it will be accepted only
  once. The main intention of this policy was to avoid {\em
    overlapping} of contributions, with clients still running an {\em
    old} run of the experiment contributing after a new one had
  started. This did not completely avoid these contributions: if the
  clients of the {\em old} run increased their new fitness, it would
  still be allowed. 
  % As I remember we kept the run_number so IPs with old runs
  % did not interfere with newer ones. But you are saying: what if they are super slow 
  % and always PUT when the run is already over?, we want to receive 
  % those individuals? 
  % "That means that if a particular IP
  % sends the fitness 99 into the server, it will be accepted only
  % once."  
  % once per run?
% JJ - once per run or experiment. But we didn't keep that run_number
% to avoid interference, just to keep track
  %  but different individuals could have the same fitness, are we limiting the search? 
% We are actually checking for the same individual, not only the fitness
  %  maybe we could have multiple versions of the pool a la MVCC  :)
% Let's leave that for the future...- JJ
  % I think if we are just trying to limit overlapping of the experiments
  % then PUTs should send the run's seq_number and completly remove it.  
% The client does not keep track of the seq number. Maybe we should do
% just that, but sending back and forth the seq number implies
% refactoring. - JJ
\end{enumerate}

@@

The baseline, called {\em base} in the
